\newcommand{\sheet}{9}
\input{Header.tex}

\begin{document}

\maketitle

\begin{exercise}{1}
    First we translate the case of finding $x, y, z \in \Z$ to finding rational
    points on $x^2 - d y^2 = 1$.

    We do exactly like in the lectures, we consider the line $L_q$ that goes
    through $(-1, 0)$ and $(0, q)$. It intersects the hyperbola at exactly one
    point. We may assume $x \geq 0$, $y \geq 0$ and $q \geq 0$, since everything
    is symmetric.

    We calculate and see that the line $L_q$ will intersect the hyperbola at the
    points $\left( \frac{1+dq^2}{1-dq^2}, \frac{2q}{1-dq^2} \right)$ and $(-1,
    0)$. Also, if we take a rational point $(x, y)$ on the curve, the line
    through it and $(-1, 0)$ will have rational slope, namely $q$ with $q =
    \frac{y}{x+1}$. That way we have a map from rational points on the curve to
    $\Q$. These two maps are each others' inverse.

    For every $q \in \Q$ we get the solution
    \begin{equation*}
        (x, y, z) = (1 + dq^2, 2q, 1 - dq^2).
    \end{equation*}
\end{exercise}

\begin{exercise}{2}
    Recall that prime ideals of $k[x, y]$ are of the following forms:
    \begin{enumerate}
        \item $(0)$
        \item $(g(y))$ for irreducible $g(y) \in (k[x])[y]$
        \item $(x - x_0, y - y_0)$ for $x_0, y_0 \in k$, and these are maximal
    \end{enumerate}

    Suppose $f(x)$ is not a square. Then $y^2 - f(x)$ is irreducible and $(y^2 -
    f(x))$ prime. Any other prime ideal containing it must then be of the third
    type. Since $k$ is algebraically closed, the only irreducible elements in
    $k[x]$ are $x - x_0$ for $x_0 \in k$. So prime ideal of the third type would
    be of the form $(x - x_0, y \pm \sqrt{f(x_0)})$. By taking square root we
    use that $k$ is algebraically closed.
    So we have
    \begin{equation*}
        \Spec\left(k[x, y] / (y^2 - f(x))\right) = \{ (x - x_0, y \pm
        \sqrt{f(x_0)}) \mid x_0 \in k \} \cup \{ (0) \}
    \end{equation*}

    Suppose now $f(x) = g^2(x)$ is a square. Then
    \begin{equation*}
        y^2 - f(x) = y^2 - g^2(x) = (y - g(x)) (y + g(x))
    \end{equation*}
    and any prime ideal would have to contain at least one of the factors. So we
    get prime ideals of the second type, namely $(y - g(x))$ and $(y + g(x))$.
    For prime ideals of the third type we get the same ones as in the previous
    case. So we get
    \begin{multline*}
        \Spec\left(k[x, y] / (y^2 - f(x))\right) = \{\, (y - g(x)), (y + g(x))
        \,\}\,\cup \\ \cup \{\, (x - x_0, y \pm \sqrt{f(x_0)}) \mid x_0 \in k \,\} \cup
        \{\,(0)\,\}
    \end{multline*}

    Lets now compute the cardinality of the fibers of the given map. First note
    that $\Spec(k[x]) = \{\, (x - x_0) \mid x_0 \in k \,\} \cup \{ (0) \}$. Take
    some $(x - x_0)$. We have to find all $p \in \Spec(k[x, y]/(y^2 - f(x)))$
    such that $p \cap k[x] = (x - x_0)$. Looking at the sets we see that there
    are two such prime ideals in $k[x, y] / (y^2 - f(x))$, namely $(x - x_0, y
    \pm \sqrt{f(x_0)})$. So the cardinality of fibers is $2$.
\end{exercise}

\end{document}
